---
title: "praca licencjacka"
author: "Zuzanna Brzóska"
date: "17 04 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(plotly)
library(pracma)
library(animation)
```

FAJNE PRZYPADKIEM:
fi = x(pi-|pi-x|), psi = x(2pi-x)


NA ODCINKU (0,2pi)

1. psi = 0
a) fi = x(2pi-x)
b) fi = pi-|pi-x|

a) fi = x(2pi-x)

```{r}
t<-0
T<-30
dt<-0.01
dx<-0.01
x<-linspace(0,2*pi,2*pi/dx)
u0<-x*(2*pi-x)
c=1
C=c*dt/dx
k<-length(u0)
u1<-u0
u1[2:(k-1)]<-u1[2:(k-1)]-(C^2)*(u0[1:(k-2)]+u0[3:k]-2*u0[2:(k-1)])/2
u<-rbind(u0,u1)
i<-2

while(t<T-dt){
  un<--u[i-1,]+2*u[i,]
  un[2:(k-1)]<-un[2:(k-1)]+(C^2)*(u[i,1:(k-2)]+u[i,3:k]-2*u[i,2:(k-1)])
  un[1]<-0
  un[length(un)]<-0
  u<-rbind(u,un)
  t<-t+dt
  i<-i+1
}

#for (i in 1:20){
#plot(u[i*100,],type='l',ylim=c(-10,10))}
```

b) fi = pi-|pi-x|

```{r}
t<-0
T<-20
dt<-0.01
dx<-0.01
x<-linspace(0,2*pi,2*pi/dx)
u0<-pi-abs(pi-x)
c=1
C=c*dt/dx
k<-length(u0)
u1<-u0
u1[2:(k-1)]<-u1[2:(k-1)]-(C^2)*(u0[1:(k-2)]+u0[3:k]-2*u0[2:(k-1)])/2
u<-rbind(u0,u1)
i<-2

while(t<T-dt){
  un<--u[i-1,]+2*u[i,]
  un[2:(k-1)]<-un[2:(k-1)]+(C^2)*(u[i,1:(k-2)]+u[i,3:k]-2*u[i,2:(k-1)])
  un[1]<-0
  un[length(un)]<-0
  u<-rbind(u,un)
  t<-t+dt
  i<-i+1
}

#for (i in 1:20){
#plot(u[i*50,],type='l',ylim=c(-3,3))}
```

1'. szeregiem
psi = 0
a) fi = x(2pi-x)
b) fi = pi-|pi-x|

$\int_0^{2\pi}x(2\pi-x)\sin(\frac{nx}{2})dx=-\frac{8}{n^3}(n\pi\sin(n\pi)+2\cos(n\pi)-2)$

$\int_0^{2\pi}(\pi-|\pi-x|)\sin(\frac{n\pi}{2})=\frac{4}{n^2}(2\sin(\frac{n\pi}{2})-\sin(n\pi))$

```{r}
f1<-function(n){
  return(-8*(n*pi*sin(n*pi)+2*cos(n*pi)-2)/(n^3))
}
f2<-function(n){
  4*(2*sin(n*pi/2)-sin(n*pi))/(n^2)
}
```

a)

```{r}
T<-20
dt<-0.01
dx<-0.01
x<-linspace(0,2*pi,2*pi/dx)
u<-rbind(c(),c())
for (l in 1:(T/dt)){
  t<-dt*l
  sum<-rep(0,length(x))
  for (n in 1:100){
    A<-f1(n)/pi
    B<-0
    step<-sin(n*x/2)*(A*cos(n*t/2)+B*sin(n*t/2))
    sum<-sum+step
  }
  u<-rbind(u,sum)
}

```

b)

```{r}
T<-50
dt<-0.01
dx<-0.01
x<-linspace(0,2*pi,2*pi/dx)
u<-rbind(c(),c())
for (l in 1:(T/dt)){
  t<-dt*l
  sum<-rep(0,length(x))
  for (n in 1:100){
    A<-f2(n)/pi
    B<-0
    step<-sin(n*x/2)*(A*cos(n*t/2)+B*sin(n*t/2))
    sum<-sum+step
  }
  u<-rbind(u,sum)
}

saveGIF({
  for (i in 1:50){
    plot(u[i*20,],type='l',main='fi=pi-|pi-x|, psi=0',ylim=c(-3,3))}
}, interval = 0.1, ani.width = 550, ani.height = 350)
```


2. fi = 0
a) psi = x(2pi-x)
b) psi = pi-|pi-x|

a) psi = x(2pi-x)

```{r}
t<-0
T<-20
dt<-0.01
dx<-0.01
x<-linspace(0,2*pi,2*pi/dx)
u0<-rep(0,length(x))
c=1
C=c*dt/dx
k<-length(u0)
u1<-u0+dt*x*(2*pi-x)
#u1<-u0
u1[2:(k-1)]<-u1[2:(k-1)]-(C^2)*(u0[1:(k-2)]+u0[3:k]-2*u0[2:(k-1)])/2
uc<-rbind(u0,u1)
i<-2

while(t<T-dt){
  #un[1]<-0
  #un[length(un)]<-un[length(un)-1]+dx
  un<--uc[i-1,]+2*u[i,]
  un[2:(k-1)]<-un[2:(k-1)]+(C^2)*(uc[i,1:(k-2)]+uc[i,3:k]-2*uc[i,2:(k-1)])
  un[1]<-0 #un[1]-dx
  un[length(un)]<-0 #un[length(un)-1]+dx
  uc<-rbind(uc,un)
  t<-t+dt
  i<-i+1
}
plot(u[1,],type='l',ylim=c(-20,20))

```

b) psi = pi-|pi-x|

```{r}
t<-0
T<-50
dt<-0.01
dx<-0.01
x<-linspace(0,2*pi,2*pi/dx)
u0<-rep(0,length(x))
c=1
C=c*dt/dx
k<-length(u0)
u1<-u0+dt*(pi-abs(pi-x))
#u1<-u0
u1[2:(k-1)]<-u1[2:(k-1)]-(C^2)*(u0[1:(k-2)]+u0[3:k]-2*u0[2:(k-1)])/2
u<-rbind(u0,u1)
i<-2

while(t<T-dt){
  #un[1]<-0
  #un[length(un)]<-un[length(un)-1]+dx
  un<--u[i-1,]+2*u[i,]
  un[2:(k-1)]<-un[2:(k-1)]+(C^2)*(u[i,1:(k-2)]+u[i,3:k]-2*u[i,2:(k-1)])
  un[1]<-0 #un[1]-dx
  un[length(un)]<-0 #un[length(un)-1]+dx
  u<-rbind(u,un)
  t<-t+dt
  i<-i+1
}
plot(u[1,],type='l',ylim=c(-5,5))

```

2'. szeregi
fi = 0
a) psi = x(2pi-x)
b) psi = pi-|pi-x|

a)

```{r}
T<-20
dt<-0.01
dx<-0.01
x<-linspace(0,2*pi,2*pi/dx)
u<-rbind(c(),c())
for (l in 1:(T/dt)){
  t<-dt*l
  sum<-rep(0,length(x))
  for (n in 1:100){
    B<-2*f1(n)/(n*pi)
    A<-0
    step<-sin(n*x/2)*(A*cos(n*t/2)+B*sin(n*t/2))
    sum<-sum+step
  }
  u<-rbind(u,sum)
}
```

b)

```{r}
T<-50
dt<-0.01
dx<-0.01
x<-linspace(0,2*pi,2*pi/dx)
u<-rbind(c(),c())
for (l in 1:(T/dt)){
  t<-dt*l
  sum<-rep(0,length(x))
  for (n in 1:100){
    B<-2*f2(n)/(n*pi)
    A<-0
    step<-sin(n*x/2)*(A*cos(n*t/2)+B*sin(n*t/2))
    sum<-sum+step
  }
  u<-rbind(u,sum)
}
saveGIF({
  for (i in 1:50){
    plot(u[i*20,],type='l',main='fi=0, psi=pi-|pi-x|',ylim=c(-5,5))}
}, interval = 0.1, ani.width = 550, ani.height = 350)
```


3.
a) fi=psi = pi-|pi-x|
b) fi=psi = x(2pi-x)
c) fi = x(2pi-x), psi = pi-|pi-x|
d) fi = pi-|pi-x|, psi = x(2pi-x)

a)

```{r}
t<-0
T<-20
dt<-0.01
dx<-0.01
x<-linspace(0,2*pi,2*pi/dx)
u0<-(pi-abs(pi-x))
c=1
C=c*dt/dx
k<-length(u0)
u1<-u0+dt*(pi-abs(pi-x))
#u1<-u0
u1[2:(k-1)]<-u1[2:(k-1)]-(C^2)*(u0[1:(k-2)]+u0[3:k]-2*u0[2:(k-1)])/2
u<-rbind(u0,u1)
i<-2

while(t<T-dt){
  #un[1]<-0
  #un[length(un)]<-un[length(un)-1]+dx
  un<--u[i-1,]+2*u[i,]
  un[2:(k-1)]<-un[2:(k-1)]+(C^2)*(u[i,1:(k-2)]+u[i,3:k]-2*u[i,2:(k-1)])
  un[1]<-0 #un[1]-dx
  un[length(un)]<-0#un[length(un)-1]
  u<-rbind(u,un)
  t<-t+dt
  i<-i+1
}

#plot(u[1,],type='l',ylim=c(-1,1),xaxt='n',xlab='x',ylab='u(x,t)')
#axis(1, at = seq(0, 200, 50), labels = c(0,0.5,1,1.5,2))
```

b)

```{r}
t<-0
T<-50
dt<-0.01
dx<-0.01
x<-linspace(0,2*pi,2*pi/dx)
u0<-x*(2*pi-x)
c=1
C=c*dt/dx
k<-length(u0)
u1<-u0+dt*x*(2*pi-x)
#u1<-u0
u1[2:(k-1)]<-u1[2:(k-1)]-(C^2)*(u0[1:(k-2)]+u0[3:k]-2*u0[2:(k-1)])/2
u<-rbind(u0,u1)
i<-2

while(t<T-dt){
  #un[1]<-0
  #un[length(un)]<-un[length(un)-1]+dx
  un<--u[i-1,]+2*u[i,]
  un[2:(k-1)]<-un[2:(k-1)]+(C^2)*(u[i,1:(k-2)]+u[i,3:k]-2*u[i,2:(k-1)])
  un[1]<-0 #un[1]-dx
  un[length(un)]<-0 #un[length(un)-1]+dx
  u<-rbind(u,un)
  t<-t+dt
  i<-i+1
}
plot(u[1,],type='l',ylim=c(-20,20))
plot(u[2,],type='l',ylim=c(-20,20))
plot(u[3,],type='l',ylim=c(-20,20))
dim(u)
for (i in 1:20){
plot(u[i*50,],type='l',ylim=c(-25,25))}

saveGIF({
  for (i in 1:50){
    plot(u[i*20,],type='l',main='fi=psi = x(2pi-x)',ylim=c(-25,25))}
}, interval = 0.1, ani.width = 550, ani.height = 350)
```

c)

```{r}
t<-0
T<-20
dt<-0.01
dx<-0.01
x<-linspace(0,2*pi,2*pi/dx)
u0<-x*(2*pi-x)
c=1
C=c*dt/dx
k<-length(u0)
u1<-u0+dt*(pi-abs(pi-x))
#u1<-u0
u1[2:(k-1)]<-u1[2:(k-1)]-(C^2)*(u0[1:(k-2)]+u0[3:k]-2*u0[2:(k-1)])/2
u<-rbind(u0,u1)
i<-2

while(t<T-dt){
  #un[1]<-0
  #un[length(un)]<-un[length(un)-1]+dx
  un<--u[i-1,]+2*u[i,]
  un[2:(k-1)]<-un[2:(k-1)]+(C^2)*(u[i,1:(k-2)]+u[i,3:k]-2*u[i,2:(k-1)])
  un[1]<-0 #un[1]-dx
  un[length(un)]<-0 #un[length(un)-1]+dx
  u<-rbind(u,un)
  t<-t+dt
  i<-i+1
}
#plot(u[1,],type='l',ylim=c(-20,20))
```

d)

```{r}
t<-0
T<-50
dt<-0.01
dx<-0.01
x<-linspace(0,2*pi,2*pi/dx)
u0<-(pi-abs(pi-x))
c=1
C=c*dt/dx
k<-length(u0)
u1<-u0+dt*x*(2*pi-x)
#u1<-u0
u1[2:(k-1)]<-u1[2:(k-1)]-(C^2)*(u0[1:(k-2)]+u0[3:k]-2*u0[2:(k-1)])/2
u<-rbind(u0,u1)
i<-2

while(t<T-dt){
  #un[1]<-0
  #un[length(un)]<-un[length(un)-1]+dx
  un<--u[i-1,]+2*u[i,]
  un[2:(k-1)]<-un[2:(k-1)]+(C^2)*(u[i,1:(k-2)]+u[i,3:k]-2*u[i,2:(k-1)])
  un[1]<-0 #un[1]-dx
  un[length(un)]<-0 #un[length(un)-1]+dx
  u<-rbind(u,un)
  t<-t+dt
  i<-i+1
}
plot(u[1,],type='l',ylim=c(-20,20))
plot(u[2,],type='l',ylim=c(-20,20))
plot(u[3,],type='l',ylim=c(-20,20))

for (i in 1:20){
plot(u[i*50,],type='l',ylim=c(-22,22))}

saveGIF({
  for (i in 1:50){
    plot(u[i*20,],type='l',main='psi= x(2pi-x), fi=pi-|pi-x|',ylim=c(-5,5))}
}, interval = 0.1, ani.width = 550, ani.height = 350)
```

3'. szeregi
a) fi=psi = pi-|pi-x|
b) fi=psi = x(2pi-x)
c) fi = x(2pi-x), psi = pi-|pi-x|
d) fi = pi-|pi-x|, psi = x(2pi-x)

a)

```{r}
T<-50
dt<-0.01
dx<-0.01
x<-linspace(0,2*pi,2*pi/dx)
u<-rbind(c(),c())
for (l in 1:(T/dt)){
  t<-dt*l
  sum<-rep(0,length(x))
  for (n in 1:100){
    A<-f2(n)/pi
    B<-2*f2(n)/(n*pi)
    step<-sin(n*x/2)*(A*cos(n*t/2)+B*sin(n*t/2))
    sum<-sum+step
  }
  u<-rbind(u,sum)
}
saveGIF({
  for (i in 1:50){
    plot(u[i*20,],type='l',main='fi=psi=pi-|pi-x|',ylim=c(-6,6))}
}, interval = 0.1, ani.width = 550, ani.height = 350)
```

b)

```{r}
T<-50
dt<-0.01
dx<-0.01
x<-linspace(0,2*pi,2*pi/dx)
u<-rbind(c(),c())
for (l in 1:(T/dt)){
  t<-dt*l
  sum<-rep(0,length(x))
  for (n in 1:100){
    A<-f1(n)/pi
    B<-2*f1(n)/(n*pi)
    step<-sin(n*x/2)*(A*cos(n*t/2)+B*sin(n*t/2))
    sum<-sum+step
  }
  u<-rbind(u,sum)
}
saveGIF({
  for (i in 1:50){
    plot(u[i*20,],type='l',main='fi=psi = x(2pi-x)',ylim=c(-25,25))}
}, interval = 0.1, ani.width = 550, ani.height = 350)
```

c)

```{r}
T<-50
dt<-0.01
dx<-0.01
x<-linspace(0,2*pi,2*pi/dx)
u<-rbind(c(),c())
for (l in 1:(T/dt)){
  t<-dt*l
  sum<-rep(0,length(x))
  for (n in 1:100){
    A<-f1(n)/pi
    B<-2*f2(n)/(n*pi)
    step<-sin(n*x/2)*(A*cos(n*t/2)+B*sin(n*t/2))
    sum<-sum+step
  }
  u<-rbind(u,sum)
}
saveGIF({
  for (i in 1:50){
    plot(u[i*20,],type='l',main='fi = x(2pi-x), psi = pi-|pi-x|',ylim=c(-12,12))}
}, interval = 0.1, ani.width = 550, ani.height = 350)
```

d)

```{r}
T<-50
dt<-0.01
dx<-0.01
x<-linspace(0,2*pi,2*pi/dx)
u<-rbind(c(),c())
for (l in 1:(T/dt)){
  t<-dt*l
  sum<-rep(0,length(x))
  for (n in 1:100){
    A<-f2(n)/pi
    B<-2*f1(n)/(n*pi)
    step<-sin(n*x/2)*(A*cos(n*t/2)+B*sin(n*t/2))
    sum<-sum+step
  }
  u<-rbind(u,sum)
}
saveGIF({
  for (i in 1:50){
    plot(u[i*20,],type='l',main='fi = pi-|pi-x|, psi = x(2pi-x)',ylim=c(-20,20))}
}, interval = 0.1, ani.width = 550, ani.height = 350)
```


fajne:
```{r}
t<-0
T<-20
dt<-0.01
dx<-0.01
x<-linspace(0,2*pi,2*pi/dx)
u0<-2*x*(pi-x)
u0[314:628]<-rep(0,315)
c=1
C=c*dt/dx
k<-length(u0)
u1<-u0+dt*u0
#u1<-u0
u1[2:(k-1)]<-u1[2:(k-1)]-(C^2)*(u0[1:(k-2)]+u0[3:k]-2*u0[2:(k-1)])/2
u<-rbind(u0,u1)
i<-2

while(t<T-dt){
  #un[1]<-0
  #un[length(un)]<-un[length(un)-1]+dx
  un<--u[i-1,]+2*u[i,]
  un[2:(k-1)]<-un[2:(k-1)]+(C^2)*(u[i,1:(k-2)]+u[i,3:k]-2*u[i,2:(k-1)])
  un[1]<-0 #un[1]-dx
  un[length(un)]<-0 #un[length(un)-1]+dx
  u<-rbind(u,un)
  t<-t+dt
  i<-i+1
}
saveGIF({
  for (i in 1:50){
    plot(u[i*20,],type='l',main='fi = pi-|pi-x|, psi = x(2pi-x)',ylim=c(-3,3))}
}, interval = 0.1, ani.width = 550, ani.height = 350)
```


```{r}
t<-0
T<-50
dt<-0.01
dx<-0.01
x<-linspace(0,2*pi,2*pi/dx)
u0<-(pi-abs(pi-2*x))
u0[314:628]<-rep(0,315)
c=1
C=c*dt/dx
k<-length(u0)
u1<-u0+dt*u0
u1[2:(k-1)]<-u1[2:(k-1)]-(C^2)*(u0[1:(k-2)]+u0[3:k]-2*u0[2:(k-1)])/2
u<-rbind(rep(0,length(x)),u1)
i<-2

while(t<T-dt){
  un<--u[i-1,]+2*u[i,]
  un[2:(k-1)]<-un[2:(k-1)]+(C^2)*(u[i,1:(k-2)]+u[i,3:k]-2*u[i,2:(k-1)])
  un[1]<-0
  un[length(un)]<-0 
  u<-rbind(u,un)
  t<-t+dt
  i<-i+1
}

for (i in 1:20){
plot(u[i*50,],type='l',ylim=c(-100,100))}

saveGIF({
  for (i in 1:50){
    plot(u[i*20,],type='l',main='fi=0, psi=pi-|pi-x|',ylim=c(-5,5))}
}, interval = 0.1, ani.width = 550, ani.height = 350)
```





NA KWADRACIE

```{r}
dx<-0.04
u0<-matrix(0,50,50)
for (i in 25:0){
  v<-sin(linspace(0,2,2/dx)*pi)*(1-i/25)
  u0[25-i,]<-v
  u0[25+i,]<-v
}
plot_ly(z=u0,type='surface')

dt<-0.1
C<-1
T<-10
t<-0
i<-2
u <- array(0,dim=c(50,50,T/dt))
u[,,1]<-u0
u1<-u0
u1[2:(k-1),2:(k-1)]<-u1[2:(k-1),2:(k-1)]-(C^2)*(u0[1:(k-2),1:(k-2)]+u0[3:k,3:k]-2*u0[2:(k-1),2:(k-1)])/2
u[,,2]<-u1

while(t<T-3*dt){
  k<-50
  un<--u[,,i-1]+2*u[,,i]
  un[2:(k-1),2:(k-1)]<-un[2:(k-1),2:(k-1)]+(C^2)*(u[,,i][1:(k-2),1:(k-2)]+u[,,i][3:k,3:k]-2*u[,,i][2:(k-1),2:(k-1)])
  un[1,]<-0
  un[,1]<-0
  un[,k]<-0
  un[k,]<-0
  u[,,i+1]<-un
  t<-t+dt
  i<-i+1
}

plot_ly(z=u[,,1],type='surface')
plot_ly(z=u[,,2],type='surface')
plot_ly(z=u[,,3],type='surface')
plot_ly(z=u[,,4],type='surface')
plot_ly(z=u[,,5],type='surface')
plot_ly(z=u[,,6],type='surface')
plot_ly(z=u[,,7],type='surface')
plot_ly(z=u[,,8],type='surface')
plot_ly(z=u[,,9],type='surface')
plot_ly(z=u[,,10],type='surface')

Y<-as.data.frame.table(u)
p<-plot_ly(Y, x =~Var1, y=~Var2, z = ~Freq, frame =~Var3, type = 'heatmap')
p
```

```{r}

library(mnormt)
x     <- seq(-5, 5, 0.25) 
y     <- seq(-5, 5, 0.25)
mu    <- c(0, 0)
sigma <- matrix(c(1, 0, 0, 1), nrow = 2)
f     <- function(x, y) dmnorm(cbind(x, y), mu, sigma)
z     <- outer(x, y, f)

plot_ly(z=z,type='surface')

u0<-z
dt<-0.1
C<-1
T<-10
t<-0
i<-2
k<-41
u <- array(0,dim=c(k,k,T/dt))
u[,,1]<-u0
u1<-u0
u1[2:(k-1),2:(k-1)]<-u1[2:(k-1),2:(k-1)]-(C^2)*(u0[1:(k-2),1:(k-2)]+u0[3:k,3:k]-2*u0[2:(k-1),2:(k-1)])/2
u[,,2]<-u1

while(t<T-3*dt){
  un<--u[,,i-1]+2*u[,,i]
  un[2:(k-1),2:(k-1)]<-un[2:(k-1),2:(k-1)]+(C^2)*(u[,,i][1:(k-2),1:(k-2)]+u[,,i][3:k,3:k]-2*u[,,i][2:(k-1),2:(k-1)])
  un[1,]<-0
  un[,1]<-0
  un[,k]<-0
  un[k,]<-0
  u[,,i+1]<-un
  t<-t+dt
  i<-i+1
}

Y<-as.data.frame.table(u)
p<-plot_ly(Y, x =~Var1, y=~Var2, z = ~Freq, frame =~Var3, type = 'heatmap')
p
```

```{r}
k<-100
x<-(0:(k-1))/(k-1)
y<-(0:(k-1))/(k-1)
dx<-1/length(x)
dy<-1/length(y)
u0<-(sin(pi*x)%*%sin(pi*t(y)))

dt<-0.1
c<-0.01
cx<-c*dt/dx
cy<-c*dt/dy
T<-100
t<-0
i<-2
u <- array(0,dim=c(k,k,T/dt))
u[,,1]<-u0
u1<-u0
u1[2:(k-1),2:(k-1)]<-u0[2:(k-1),2:(k-1)]+0.5*(cx^2)*(u0[3:k,2:(k-1)]-2*u0[2:(k-1),2:(k-1)]+u0[1:(k-2),2:(k-1)])+0.5*(cy^2)*(u0[2:(k-1),3:k]-2*u0[2:(k-1),2:(k-1)]+u0[2:(k-1),1:(k-2)])
u[,,2]<-u1

while(t<T-3*dt){
  un<--u[,,i-1]+2*u[,,i]
  un[2:(k-1),2:(k-1)]<-un[2:(k-1),2:(k-1)]+(cx^2)*(u[,,i][1:(k-2),2:(k-1)]+u[,,i][3:k,2:(k-1)]-2*u[,,i][2:(k-1),2:(k-1)])+(cy^2)*(u[,,i][2:(k-1),1:(k-2)]+u[,,i][2:(k-1),3:k]-2*u[,,i][2:(k-1),2:(k-1)])
  un[1,]<-0
  un[,1]<-0
  un[,k]<-0
  un[k,]<-0
  u[,,i+1]<-un
  t<-t+dt
  i<-i+1
}
p<-plot_ly(z=u[,,1],type='surface')
p<-layout(p, scene = list(zaxis = list(range = c(-1,1))))
p
p<-plot_ly(z=u[,,300],type='surface')
p<-layout(p, scene = list(zaxis = list(range = c(-1,1))))
p
p<-plot_ly(z=u[,,500],type='surface')
p<-layout(p, scene = list(zaxis = list(range = c(-1,1))))
p
p<-plot_ly(z=u[,,800],type='surface')
p<-layout(p, scene = list(zaxis = list(range = c(-1,1))))
p


```

